\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-02-07 tex/introduction.tex
'Merge' introduction from 'science' branch

@@

Some conclusions derived from this approach may be sensitive to the probability distribution from which the strengths of interconnection are sampled, whereas others are independent of the specific form of this distribution. In the former case, discovering the constraints that contribute to determining the functional form of the distribution can be a matter for empirical investigation and results that are themselves functions of this distribution can be reinterpreted in light of ongoing updates from relevant empirical observations. On the other hand, results that are independent of the specific form of this distribution can be expected to hold in any case and a specific distribution may simply be chosen for the purposes of exemplifying the result.

>>>>

% Some conclusions derived from this approach may be sensitive to the probability distribution from which the strengths of interconnection are sampled, whereas others are independent of the specific form of this distribution. In the former case, discovering the constraints that contribute to determining the functional form of the distribution can be a matter for empirical investigation and results that are themselves functions of this distribution can be reinterpreted in light of ongoing updates from relevant empirical observations. On the other hand, results that are independent of the specific form of this distribution can be expected to hold in any case and a specific distribution may simply be chosen for the purposes of exemplifying the result.

@@
